---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Ignacio Ojea Quintana"
date: "3/27/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60)
)
```

## Problem Description

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server.
3. Share the application link by pasting it into the provided text box.
4. Share your server.R and ui.R code on github.

## Response

I will plot some statistics about COVID-19 using the Johns Hopkins University github repo:  https://github.com/CSSEGISandData/COVID-19

I will be using the latest data available to the date.

The application is running on: https://ignacio-ojea.shinyapps.io/Final-Project/

ui.R, and Server.R Code, plus data sets, in my github repository: https://github.com/IgnacioOQ/Developing-Data-Products

## How to use the application

On the first tab, the plot shows number of confirmed, recovered, and death cases by selected country. 

On the second tab, the plot shows a forecast for the next ten days using an exponential smoothing state space model (ets) from the forecast package. This is clearly not the best predictive method for the case, but it is a start.

```{r, echo=FALSE}
library(plotly)
library(reshape2)
library(data.table)
library(tidyr)
library(countrycode)
```

```{r, echo=FALSE}
setwd('C:/Users/Ignacio/Google Drive/Cursos Online/Data Science/Developing Data Products/Week 2/Johns Hopkins Corona Repository/csse_covid_19_data/csse_covid_19_time_series')
timeseriesconfirmed <- read.csv("time_series_covid19_confirmed_global.csv")
timeseriesdead <- read.csv("time_series_covid19_deaths_global.csv")
timeseriesrecovered <- read.csv("time_series_covid19_recovered_global.csv")
```

```{r, warning=FALSE, message=FALSE, results='hide', echo=FALSE}
# I'll add as latitude and longitude for the Total the location of Hubei, where the city of Wuhan is
addtotal <- function(df){
  sums <- colSums(df[,5:ncol(df)])
  levels(df[,1]) <- c(levels(df[,1]),"Total")
  levels(df[,2]) <- c(levels(df[,2]),"Total")
  totalsums <- c("Total","Total",30.97560,112.270700,sums)
  df[nrow(df)+1,] <- totalsums
  return(df)}
getseries <- function(df){
  total <- df[nrow(df),5:ncol(df)]
  total <- as.data.frame(t(total))
  total[,1] <- as.numeric(as.character(total[,1]))
  return(total)
}
timeseriesconfirmed <- addtotal(timeseriesconfirmed)
timeseriesdead <- addtotal(timeseriesdead)
timeseriesrecovered <- addtotal(timeseriesrecovered)
seriesconfirmed <- getseries(timeseriesconfirmed)
seriesdead <- getseries(timeseriesdead)
seriesrecovered <- getseries(timeseriesrecovered)
total <- cbind(seriesconfirmed,seriesdead,seriesrecovered)
colnames(total) <- c("Confirmed", "Dead", "Recovered")
# Parte bien dificil, gather es dificil de usar, no se hacerlo sin transformar rownames to column
# Rownames to column
totalgathered <- total
rownames(total) <- 1:nrow(total)
setDT(total, keep.rownames = TRUE)[]
setDT(totalgathered, keep.rownames = TRUE)[]
# Gather
totalgathered <- gather(totalgathered,"Status", "Amount",-rn)
totalgathered$Status <- as.factor(totalgathered$Status)
```

## Plotting Totals

This plot is just an example obtained from the data set, aggregating the global total cases.

```{r, echo=FALSE}
# First Plot
# Ahora plotear
fig <- plot_ly(totalgathered, y = totalgathered$Amount, color = ~Status, type = "scatter", mode = "lines")
fig <- fig %>% layout(
    title = "Coronavirus Count", xaxis = list(title = "Days Since January 22nd"),
      yaxis = list(title = "Count"))
fig
```

