---
title: "Statistical Inference Project Pt 2"
author: "Hsin Chih Chen"
date: "10/6/2021"
output: html_document
---

## Introduction

The ToothGrowth data in R datasets will be analyzed accordingly to find the data summary and use hypothesis tests to compare the tooth growth factor by either the supplement type and does type.

## Preliminary Setup & Store Data

```{r}
# load graphing tool interface package
library(ggplot2)

# initialize data category
Tooth <- ToothGrowth
```

## Provide Initial Summaries for the data structure.
```{r}
# General summaries for the data frame
summary(Tooth)

# Examine the characteristics for each section
str(Tooth)
```

## Plot Tooth grow length and dose by splitting the supplement
```{r}
# Use boxplot by having the classified grid for supplement
  ggplot(aes(x = as.factor(dose),y = len), data = Tooth) +     geom_boxplot(aes(fill = dose)) + 
  xlab("Dose (mg)") + 
  ylab("Tooth Length")+ 
  facet_grid(~ supp) + 
  ggtitle("Tooth Length & Dose Amount by Supplement")
```

## Plot Tooth grow length and supplement by splitting the dosage amount
```{r}
# Use boxplot by having the classified grid for dosage
  ggplot(aes(x = supp,y = len), data = Tooth)+ 
  geom_boxplot(aes(fill = supp)) + 
  xlab("Supplement") + 
  ylab("Tooth Length") + 
  facet_grid(~ dose) + 
  ggtitle("Tooth Length & Dose Amount by Dosage")
```

## Have Initial Hypothesis Test for the supplement classification

In this Hypothesis testing, the following hypothesis test is listed below:

H0 = Both supplement will generate the same impact towards tooth length growth.
H1 = Both supplement will generate different impact towards tooth length growth.

```{r}
# Use 2 sample t-test to compare
t.test(len ~ supp, data = Tooth)
```

## Have Initial Hypothesis Test for the dosage classification

In this Hypothesis testing, the following hypothesis test is listed below:

H0 = Both dosage will generate the same impact towards tooth length growth.
H1 = Both dosage will generate different impact towards tooth length growth.

```{r}
# Use 2 sample t-test to compare where the dosage is 0.5 and 1
Tooth1 <- subset(Tooth, Tooth$dose %in% c(0.5,1))
t.test(len ~ dose, data = Tooth1)
```

```{r}
# Use 2 sample t-test to compare where the dosage is 1 and 2
Tooth2 <- subset(Tooth, Tooth$dose %in% c(1,2))
t.test(len ~ dose, data = Tooth2)
```

```{r}
# Use 2 sample t-test to compare where the dosage is 0.5 and 2
Tooth3 <- subset(Tooth, Tooth$dose %in% c(0.5,2))
t.test(len ~ dose, data = Tooth3)
```

## Statistical Conclusion

Based on the t-test results and p-value description, the following conclusions are made.

1. Supplement type will NOT contribute different impact towards the tooth length based on the given p-value. 


2. Dosage type will contribute different impact towards the tooth length based on the given p-value across all 3 factors of dosage. (H0 was rejected)