---
title: 'Data Visualization Capstone: Data Review'
author: "Hsin Chih Chen"
date: "2022/4/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(lubridate)
```

## Data Import

Applying read.csv function while identifying the NA items, then use na.omit to 
ensure the remaining data set has complete entries for all 10 variables.

```{r Data Import & Wrangling}
# Obtain Raw Data from Source
URL <- "https://data.cityofchicago.org/api/views/qmqz-2xku/rows.csv?accessType=DOWNLOAD"
download.file(URL,"bwq.csv",method = "curl")

# Execute Data Import while removing the missing data entries.
dat <- read.csv("bwq.csv", header = TRUE, na.strings = c("","NA","0",0)) 
dat$Measurement.Timestamp <- parse_date_time(dat$Measurement.Timestamp, "mdy_HMS")

# Rename Beach to Simplify Beach Names
beach <- recode(dat$Beach.Name, "63rd Street Beach" = "63rd Street", "Calumet Beach" = "Calumet", "Montrose Beach" = "Montrose", "Ohio Street Beach" = "Ohio Street", "Osterman Beach" = "Osterman", "Rainbow Beach" = "Rainbow")

# Replace Parameter Name after Recode
dat$Beach.Name <- beach

# Mutate with respective year and month
dat <- dat %>%
  mutate(year = year(Measurement.Timestamp), month = month(Measurement.Timestamp)) %>%
  select(-Transducer.Depth) %>%
  filter(Wave.Height > 0) %>%
  arrange(Measurement.Timestamp)

dat$year <- as.character(dat$year)
dat$month <- as.character(dat$month)

# Clean Data with na.values
tidy <- na.omit(dat)
```

## Graph 1

This graph is to use the ggplotly to demonstrate the distribution quartile range for ohio street beach's water temperature from 2014 to 2021. The x axis contains the individual beach while the y axis is the water temperature in celsius.

The following code chunk illustrates how I generated my data set for graph illustration.

```{r Graph 1}
# Select & Demonstrate the Structure of Tibble
data1 <- tidy %>%
  filter(Beach.Name == "Ohio Street") %>%
  filter(year !=　"2013")

# Examine Data Structure
as_tibble(data1)

# Plot Graph
ggplotly(graph1 <- data1 %>%
  ggplot(aes(x = year, y = Water.Temperature, fill = year)) +
    geom_boxplot()+
      theme(axis.text.y = element_text(size = 8),
            axis.text.x = element_text(size = 8),
            axis.title = element_text(size = 8, face = "bold"),
            title = element_text(size =10, face = "bold"),
            legend.title = element_text(size = 8),
            legend.text = element_text(size = 6),
            legend.key.width = unit(0.5, 'cm'),
            legend.key.height = unit(0.5, 'cm'),
            legend.key.size = unit(0.5, 'cm')) + 
      labs(x = "Year", y = "Temperature (Celsius)", title = "Water Temperature for Ohio Street Beach by Years"))
```

## Graph 2

This graph is to use the ggplotly to demonstrate the distribution density for individual beach's wave height in 2015. The x axis contains the individual beach while the y axis is the wave height in meters.

The following code chunk illustrates how I generated my data set for graph illustration.

```{r Graph 2}
# Select & Demonstrate the Structure of Tibble
data2 <- tidy %>%
  filter(year == "2015")
  

# Examine Data Structure
as_tibble(data2)

# Plot Graph
ggplotly(graph2 <- data2 %>%
           ggplot(aes(x = Beach.Name, y = Wave.Height, fill = Beach.Name)) +
           geom_violin()+ 
           theme(axis.text.y = element_text(size = 8),
                 axis.text.x = element_text(size = 8),
                 axis.title = element_text(size = 8, face = "bold"),
                 title = element_text(size =10, face = "bold"),
                 legend.title = element_text(size = 8),
                 legend.text = element_text(size = 6),
                 legend.key.width = unit(0.5, 'cm'),
                 legend.key.height = unit(0.5, 'cm'),
                 legend.key.size = unit(0.5, 'cm')) + 
           labs(x = "Chicago Beach Location", y = "Wave Height (m)", title = "Chicago's 2015 Wave Height Distribution Coparison"))
```

## Graph 3

This graph is to use the ggplotly to show average turbidity level for individual beach in 2015. The x axis contains the turbidity level in Nephelometric Turbidity Units (NTU) while y axis is the individual beach.

The following code chunk illustrates how I generated my data set for graph illustration.

```{r Graph 3}
# Select & Demonstrate the Structure of Tibble
data3 <- tidy %>%
    filter(year == "2015")

# Examine Data Structure
as_tibble(data3)

# Plot the Graph
ggplotly(graph3 <- data3 %>%
           select(Turbidity,Beach.Name) %>%
           group_by(Beach.Name) %>%
           summarize(avg_turbidity = mean(Turbidity)) %>%
           ggplot(aes(x = avg_turbidity, y = Beach.Name))+
           geom_point(color = 'red', size = 2)+
           geom_segment(aes(x = 0, xend = avg_turbidity,y = Beach.Name, yend = Beach.Name), color = "blue") + 
           theme(axis.text.y = element_text(size = 8),
                 axis.text.x = element_text(size = 8),
                 axis.title = element_text(size = 8, face = "bold"),
                 title = element_text(size =10, face = "bold")) + 
           labs(y = "Chicago Beach Location", x = "Average Turbidity (NTU)", title = "Average Turbidity Level Calculated in 2015"))
```
