---
title: "Data Products - Plotly"
author: "Hsin Chih Chen"
date: "10/19/2021"
output: ioslides_presentation
---

## Project Description
This project will demonstrate the `plotly` package's practice and demonstrate with the datasets built within in R for description. 

In this case, I have selected the air quality data (removing the NA values) to evaluate the comparison by months for wind level and Ozone level. 

```{R Library Loading, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
library(tidyr)
```

## Data Cleaning & Arrangement for Air Quality
```{R Data Sorting, warning=FALSE, message=FALSE, echo=TRUE}
# Remove NA items for the data
air_clean <- na.omit(airquality)

# Convert the Month as factors to classify the setup
air_clean$Month <- as.factor(air_clean$Month)
```

## Use Box Plot to demonstrate the Ozone level by Month

```{r, warning=FALSE, message=FALSE, echo=FALSE}
format(Sys.time())
plot_ly(air_clean, x = air_clean$Month, y=air_clean$Ozone, color=air_clean$Month, type="box")%>% 
  layout(title='Ozone Level by Month')
```

## Use Box Plot to demonstrate the wind level by Month

```{r, warning=FALSE, message=FALSE, echo=FALSE}
format(Sys.time(), "%a %b %d %X %Y")
plot_ly(air_clean, x = air_clean$Month, y=air_clean$Wind, color=air_clean$Month, type="box")%>% 
  layout(title='Wind Level by Month')
```
