---
title: "Data Visualization in R with ggplot2: Week 1 Review"
date: "2022/04/02"
output: html_document
---

```{r setup, include=FALSE}
######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Center of Legislative Effectiveness Data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Hsin Chih Chen

**IMPORTANT: Filter your data so you are only displaying information for the 115th Congress.**

## Exercise 1

Hints:

* For the y-axis, use the variable "all_pass".

* For the x-axis, use the variable "dwnom1".

* Make sure you recode the data for the "female" variable and rename it as "Gender" to generate the correct labels for the legend.

* Set the color aesthetic in the ggplot() function to make the color of the dots change based on Gender.

* Make sure the axis labels are correct.

```{r exercise1,echo=FALSE}
# Recode the binary variable as strings
classify <- recode(cel$female, `0` = "Male", `1` = "Female")

# Restore into the data frame
cel$female <- classify

# Execute the rename for the gender column
cel <- cel %>%
  rename(Gender = female)

# Filter for the 115th congress
cel1 <- cel %>%
  filter(congress == 115)

# Execute gg plot with scatter points with description
  ggplot(data = cel1, aes(x = dwnom1, y = all_pass, color = Gender)) +   
           geom_point() +
           labs(x = "Ideology", y = "Bills Passed")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "votepct".

* For the y-axis, use "all_pass".

* Make sure you recode the data for the "female" variable to generate the correct labels for the legend. Rename that column "Gender". (you may have already done this in the last exercise)

* Make sure you recode the data for "majority" variable to generate the correct labels of the facetted figures.

* Set the color aesthetic in the ggplot() function to make the color of the dots change based on Gender.

* Use scale_color_manual() to set the colors to green for males and orange for females.

* Make sure the axis labels are correct.


```{r exercise2,echo=FALSE}
# Recode the majority and minority
popu <- recode(cel$majority, `0` = "Minority", `1` = "Majority")

# Re-load the inserted strings
cel$majority <- popu

# Same filter for the 115th congress
cel2 <- cel %>%
  filter(congress == 115)

# Plot based on the vote percentage and change colors manually
  ggplot(data = cel2, aes(x = votepct, y = all_pass, color = Gender)) +   
           geom_point() +
           labs(x = "Vote Percentage", y = "Bills Passed") +
           facet_wrap(.~cel2$majority) +
           scale_color_manual(values= c("orange", "green"))
```

## Exercise 3

Hints:

* For the y-axis, use the variable "les".

* Make sure you recode the data for the "majority" variable to generate the correct labels. (you may have already done this in the last exercise)

* Make sure the axis labels and figure title are correct.


```{r exercise3,echo=FALSE}
# Plot boxplot for the legislative effectiveness via group type
ggplot(data = cel2, aes(x = majority, y = les)) +   
           geom_boxplot() +
           labs(x = "Majority or Minority", y = "Legislative Effectiveness") +
           ggtitle("LES in the 115th Congress")
```
