---
title: "Week 3 Peer Review"
output: html_document
---

[Week 3 Peer Preview Output Link](https://rpubs.com/hsc251/JHU_DataVis_ggplot_3)

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))


```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Hsin Chih Chen

## Exercise 1

Explain what you are visualizing here:

In this exercise, I have generated random temperature between 15 to 30 degrees Celsius for Taiwan's major cities in year 2020. The line plot shows each city's temperature trend respectively.

Put your figure here:

```{r exercise1,echo=FALSE}
# Generate necessary vectors before compile into data frame
monthly <- rep(c(1:12), each = 6)
location <- c("Taipei", "Taichung", "Tainan", "Kaoshiung", "Changhua", "Miaoli")
temperature <- runif(n = 72, min = 15, max = 30)

# place into data frame
temper_trend <- data.frame(monthly, location, temperature)

# Generate Trend Plot for Grades
ggplot(data = temper_trend, aes(x = monthly, y = temperature, color = location)) + 
  geom_line()+
  facet_wrap(.~ location)+
  ggtitle("Taiwan's City Temperature Trend in 2020")+
  labs(x = "Month",y = "Temperature (Celsius)") + 
  theme(legend.position = "none")
```

## Exercise 2

Explain what you are visualizing here:

This histogram will demonstrate the weight distribution for the Taiwan adult males range from age 15 to age 60. 

Put your figure here:

```{r exercise2,echo=FALSE}
weight <- runif(n = 300, min = 50, max = 150)
candidate <- seq(from = 1, to = 300,1)
weight_sum <- data.frame(candidate, weight)
ggplot(data = weight_sum, aes(x = weight)) +
  geom_histogram(color = '#666666', fill = '#82E9F2') + 
  labs(x = "Weight (kg)", y = "Count") + 
  theme(legend.position = "none") +
  ggtitle("Taiwan Male Weight Distribution between age 15 and 60")

```

## Exercise 3

Explain what you are visualizing here:
This graph shows the scatter plot which demonstrate the correlation between the PM 2.5 level and Ozone level for Tamsui District's air quality level located in Taiwan. Light theme was applied for this plot.

Put your figure here:

```{r exercise3,echo=FALSE}
# Import the Air Quality for Tamsui throughout the 2020 interval
TS_Raw <- read.csv("TS2020.csv", na.strings = c("NA",0,"0"), header = TRUE)

# Transit the data variable to compare
TS_Raw$PM2.5 <- as.numeric(TS_Raw$PM2.5)
TS_Raw$O3 <- as.numeric(TS_Raw$O3)

# plot
ggplot(data = TS_Raw, aes(x = PM2.5, y = O3)) +
  geom_point(color = '#BB0000') + 
  labs(x = "PM2.5 Level", y = "O3 Level") + 
  ggtitle("Tamsui 2020 PM 2.5 vs O3 Summary") +
  theme_light()
  
```

## Exercise 4

Explain what you are visualizing here:

This plot is using the cces dataset while recoding the education level and region, then plot the region's population count based on education level.

Put your figure here:

```{r exercise4,echo=FALSE}
# Recode the education and region variable
edu <- recode(cces$educ, `1` = "No High School", `2` = "High School Grad", `3` = "Some College", `4` = "2-Years", `5` = "4-Years", `6` = "Post-Grad")

area <- recode(cces$region, `1` = "Northwest", `2` = "Midwest", `3` = "South", `4` = "West")

# Rename the education variable
cces$educ <- edu
cces$region <- area

# Plot the Region's population based on education split
ggplot(data = cces, aes(x = region, fill = edu)) +
  geom_bar(stat = "count") +
  labs (x = "Region", y = "Count") +
  ggtitle("Region Population based on Education Level") +
  guides(fill = guide_legend(title = "Edu. Level"))
```
