---
title: 'Data Visualization in R with ggplot2: Week 3 Peer Review'
author: "Hsin Chih Chen"
date: "2022/4/2"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))


```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Hsin Chih Chen

## Exercise 1

Explain what you are visualizing here:

In this exercise, I have generated random temperature between 15 to 30 degrees Celsius for Taiwan's major cities in year 2020. The line plot shows each city's temperature trend respectively.

Put your figure here:

```{r exercise1,echo=FALSE}
# Generate necessary vectors before compile into data frame
monthly <- rep(c(1:12), each = 6)
location <- c("Taipei", "Taichung", "Tainan", "Kaoshiung", "Changhua", "Miaoli")
temperature <- runif(n = 72, min = 15, max = 30)

# place into data frame
temper_trend <- data.frame(monthly, location, temperature)

# Generate Trend Plot for Grades
ggplot(data = temper_trend, aes(x = monthly, y = temperature, color = location)) + 
  geom_line()+
  facet_wrap(.~ location)+
  ggtitle("Taiwan's City Temperature Trend in 2020")+
  labs(x = "Month",y = "Temperature (Celsius)") + 
  theme(legend.position = "none")
```
