---
title: "Week 2 Peer Review"
output: html_document
---

[Week 2 Peer Preview Output Link](https://rpubs.com/hsc251/JHU_DataVis_ggplot_2)

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Hsin Chih Chen



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
# Recode the ideology variable
party <- recode(cces$ideo5, `1` = "Very Liberal", `2` = "Liberal", `3` = "Moderate", `4` = "Conservative", `5` = "Very Conservative")

# Rename the ideology variable
cces$ideo5 <- party

# Plot the bar charts while get the identity
ggplot(data = cces, aes(x = ideo5, fill = ideo5)) +
  geom_bar(stat = "count") +
  labs (x = "Ideology", y = "Count") +
  theme(legend.position = "none") + 
  ggtitle("Respondent Ideology")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
# Recode religion names
religion <- recode(cces$pew_religimp, `1` = "Very imp.", `2` = "Somewhat imp.", `3` = "Not too imp.", `4` = "Not imp.")

# Rename the religion impact variable
cces$pew_religimp <- religion


# Plot the bar charts while get the identity
ggplot(data = cces, aes(x = pew_religimp, fill = ideo5)) +
  geom_bar(stat = "count") +
  labs (x = "Importance of Religion", y = "Count") +
  ggtitle("Importance of Religion by Ideology") +
  guides(fill = guide_legend(title = "Ideology"))
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
# Generate necessary vectors before compile into data frame
semester <- rep(c(1:6), each = 3)
students <- c("Amanda", "Betty", "Carol")
grades<- runif(n = 18, min = 80, max = 100)

# place into data frame
grade_trend <- data.frame(semester, students,grades)

# Generate Trend Plot for Grades
ggplot(data = grade_trend, aes(x = semester, y = grades, color = students)) + 
  geom_line()+
  facet_wrap(.~ students)+
  ggtitle("Student Grades by Semester")+
  labs(x = "Semester",y = "Grade") + 
  theme(legend.position = "none")
```
