---
title: "Spatial Figures Peer Review"
output: html_document
---
# Hsin Chih Chen

## Problem 1

Create the following figure, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

library(tidyverse)
library(maps)

####make some data for painting the map

my_world_map <- map_data("world")

countries <- unique(my_world_map$region)

set.seed(987)
some_data_values <- data.frame(

  "region"=countries,
  
  "Score"=runif(252,0,100))

```

```{r problem_1,echo=FALSE,message=FALSE}

####Make sure you install any necessary libraries
####HINT: Use the following code to get the colors right
#scale_fill_distiller(palette=5)

####HINT: make sure you use left_join to combine the data_values above to the world map data in my_world_map

new_world <- left_join(my_world_map, some_data_values, by = "region")

ggplot(data = new_world, mapping = aes(x = long, y = lat, group = group, fill = Score)) + 
  geom_polygon() + 
  labs(x = "long", y = "lat") + 
  scale_fill_distiller(palette = 5)
```

## Problem 2

Create the following figure, using the data included in the R Markdown file.


```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
set.seed(15)
Measurement<-rnorm(32,50,1)
```


```{r solution_p2,echo=FALSE,message=FALSE}

####Make sure you load any necessary libraries

####HINT: Use a filter command to get just maps of Costa Rica, Panama, and Nicaragua

world <- map_data("world")

south_america <- world %>%
  filter(region == "Panama" | region == "Costa Rica" | region == "Nicaragua")
  
cities <- maps::world.cities
sa_cities <- cities %>%
  filter(country.etc == "Panama" | country.etc == "Costa Rica" | country.etc == "Nicaragua") %>%
  filter(pop > 40000) %>%
  mutate(Measurement = Measurement)

ggplot(data = south_america, mapping = aes(x = long, y = lat, group = group)) + 
  geom_polygon(fill = "white", color = "black") + 
  geom_point(data = sa_cities, aes(x = long, y = lat, group = NULL, color = Measurement, size = 5)) + 
  scale_color_distiller(palette=7) +
  scale_size(guide = NULL)

####Hint: Use a filter command to put in points only for cities with a population of greater than 40,000. This should leave you with 32 cities.

####Hint: Use add_column to attach the "Measurement" variable to your data, and set that to the color aesthetic when you draw the points.

####Hint: set the colors for the city points with scale_color_distiller(palette=7)

####Hint: set the size of all points to the value 5


```

## Problem 3

Create the following figure, using the data included in the R Markdown file.

Note that the code in the .rmd file will import a set of simple features data for South America. Make sure you install any necessary packages. 

```{r problem_3_data,include=FALSE}

#####INSTALL THESE PACKAGES IF NECESSARY
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)

####DO NOT MODIFY
s_america<-ne_countries(scale="medium",continent='south america',returnclass="sf")

```

```{r problem3,echo=FALSE}

####Make sure you load any necessary libraries

####HINT: the s_america object created in the chunk above is a simple features object with many columns. Identify the correct column based on the solution figure and use it to color in the choropleth.

####HINT: Use scale_fill_distiller and palette 10 to the match the colors.

####PUT YOUR CODE HERE
ggplot(s_america) + geom_sf(aes(fill = pop_est)) +
  scale_fill_distiller(palette = 10)

```


