---
title: "Hsin Chih's Data Visual Capstone"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: journal
runtime: shiny
---


```{r Setup & Wrangle}
## Load the required Packages
library(flexdashboard)
library(tidyverse)
library(plotly)
library(shiny)
library(dplyr)
library(lubridate)

# Obtain Raw Data from Source
URL <- "https://data.cityofchicago.org/api/views/qmqz-2xku/rows.csv?accessType=DOWNLOAD"
download.file(URL,"bwq.csv",method = "curl")

# Execute Data Import while removing the missing data entries.
dat <- read.csv("bwq.csv", header = TRUE, na.strings = c("","NA","0",0)) 
dat$Measurement.Timestamp <- parse_date_time(dat$Measurement.Timestamp, "mdy_HMS")

# Rename Beach to Simplify Beach Names
beach <- recode(dat$Beach.Name, "63rd Street Beach" = "63rd Street", "Calumet Beach" = "Calumet", "Montrose Beach" = "Montrose", "Ohio Street Beach" = "Ohio Street", "Osterman Beach" = "Osterman", "Rainbow Beach" = "Rainbow")

# Replace Parameter Name after Recode
dat$Beach.Name <- beach

# Mutate with respective year and month
dat <- dat %>%
  mutate(disp_year = year(Measurement.Timestamp), disp_month = month(Measurement.Timestamp)) %>%
  mutate(year_month = paste(disp_year, disp_month, sep = "_")) %>%
  select(-Transducer.Depth) %>%
  filter(Wave.Height > 0) %>%
  arrange(Measurement.Timestamp)
dat$disp_year <- as.character(dat$disp_year)
dat$disp_month <- as.character(dat$disp_month)

# Clean Data with na.values
tidy <- na.omit(dat)

# Generate the factors for filtering
year_factor <- seq(min(tidy$disp_year),max(tidy$disp_year),1)
wave_year <- c(2014, 2015, 2016, 2018, 2019, 2020, 2021)
beach_factor <- unique(tidy$Beach.Name)
```

Summary
======

Column
------

**Background**: </br>

</br>

The data was gathered from the city of Chicago's beach data accumulated from 2013 to 2021 during the summer time. Data filtering and ensure the correct data was displayed to ensure no missing data or zeroes presented. </br>

</br>

**Datalink**: </br>
https://data.cityofchicago.org/Parks-Recreation/Beach-Water-Quality-Automated-Sensors/qmqz-2xku </br>

</br>

**Abstract**": </br>
The following graph has been broken down to 4 different sections to analyze. </br>

</br>

1. Beach Temperature </br>
2. Beach Wave </br>
3. Beach Turbidity </br>
4. Beach Battery Life  </br>

*Remark: Some data in 2013 were missing for some characteristics so it was neglected for data filtering*

Temperature
======


Input{.sidebar}
-----------------
### Temperature Graph Input

```{r Temperature Plot Input}
selectInput(inputId = "beach_temp",
            label = "Select the beach to display for temperature progress",
            choices = beach_factor,
            multiple = FALSE,
            selected = beach_factor[2])

sliderInput(inputId = "year_temp",
            label = "Select the year to display for individual beach's average temperature",
            min = min(year_factor),
            max = max(year_factor),
            value = year_factor[1])
```

Column
------
### Chicago Beaches' Temperature Distribution by Years
```{r Graph 1 Setup}
renderPlotly(
ggplotly(graph1 <- tidy %>%
  filter(Beach.Name %in% input$beach_temp & disp_year >= "2014") %>%
  ggplot(aes(x = disp_year, y = Water.Temperature, fill = disp_year)) +
    geom_boxplot()+
      theme(axis.text.y = element_text(size = 9),
            axis.text.x = element_text(size = 9),
            axis.title = element_text(size = 9, face = "bold"),
            title = element_text(size =10, face = "bold"),
            legend.title = element_text(size = 9),
            legend.text = element_text(size = 9),
            legend.key.width = unit(0.5, 'cm'),
            legend.key.height = unit(0.5, 'cm'),
            legend.key.size = unit(0.5, 'cm'),
            legend.position = "none") + 
      labs(x = "Year", y = "Temperature (Celsius)"))
)
```

Column
------
### Chicago Beaches' Temperature Average by Years
```{r Graph 2 Setup}
renderPlotly(
ggplotly(graph2 <- tidy %>%
           filter(disp_year == input$year_temp) %>%
           select(Water.Temperature,Beach.Name) %>%
           group_by(Beach.Name) %>%
           summarize(avg_watertemp = mean(Water.Temperature)) %>%
           ggplot(aes(x = avg_watertemp, y = Beach.Name))+
           geom_point(color = '#2F8C81', size = 2)+
           geom_segment(aes(x = 0, xend = avg_watertemp,y = Beach.Name, yend = Beach.Name), color = "red") + 
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size = 9, face = "bold"),
                 legend.position = "none") + 
           labs(y = "Chicago Beach Location", x = "Average Temperature (Celsius)")
         )
)
```



Wave
======


Input{.sidebar}
-----------------
### Wave Graph Input

```{r Wave Plot Input}
selectInput(inputId = "year_wave",
            label = "Select the year to observe the yearly progress for individual beach's wave height distribution",
            choices = wave_year,
            multiple = FALSE,
            selected = wave_year[1])

selectInput(inputId = "beach_wave",
            label = "Select the beach to observe the wave period's distribution",
            choices = beach_factor,
            multiple = FALSE,
            selected = beach_factor[3])
```

Column
------
### Chicago Beaches' Yearly Wave Height's Distribution
```{r Graph 3 Setup}
renderPlotly(
ggplotly(graph3 <- tidy %>%
           filter(disp_year == input$year_wave) %>%
           ggplot(aes(x = Beach.Name, y = Wave.Height, fill = Beach.Name)) +
           geom_violin()+ 
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size =9, face = "bold"),
                 legend.title = element_text(size = 9),
                 legend.text = element_text(size = 9),
                 legend.key.width = unit(0.5, 'cm'),
                 legend.key.height = unit(0.5, 'cm'),
                 legend.key.size = unit(0.5, 'cm'),
                 legend.position = "none") + 
           labs(x = "Chicago Beach Location", y = "Wave Height (m)")
         )
)
```

Column
------
### Chicago Beaches' Yearly Wave Period's Distribution
```{r Graph 4 Setup}
renderPlotly(
ggplotly(graph4 <- tidy %>%
           filter(Beach.Name == input$beach_wave) %>%
           filter(disp_year != "2013" & disp_year != "2017") %>%
           select(Wave.Period,disp_year) %>%
           ggplot(aes(x = disp_year, y = Wave.Period, fill = disp_year)) +
           geom_violin()+
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size = 9, face = "bold"),
                 legend.title = element_text(size = 9),
                 legend.text = element_text(size = 9),
                 legend.key.width = unit(0.5, 'cm'),
                 legend.key.height = unit(0.5, 'cm'),
                 legend.key.size = unit(0.5, 'cm'),
                 legend.position = "none") + 
           labs(x = "Chicago Beach Location", y = "Wave Period"))
)
```

Turbidity
======

Input{.sidebar}
-----------------
### Turbidity Graph Input
```{r Turbidity Plot Input}
sliderInput(inputId = "year_turb",
            label = "Select the year to observe the yearly progress for individual beach's average turbidity",
            min = min(year_factor),
            max = max(year_factor),
            value = year_factor[1])

selectInput(inputId = "beach_turb",
            label = "Select the beach to observe the turbidity's year by month average",
            choices = beach_factor,
            multiple = FALSE,
            selected = beach_factor[1])
```

Column
------
### Yearly Chicago Beach's Turbidity Averages

```{r Graph 5 Setup}
renderPlotly(
ggplotly(graph5 <- tidy %>%
           filter(disp_year == input$year_turb) %>%
           select(Turbidity,Beach.Name) %>%
           group_by(Beach.Name) %>%
           summarize(avg_turbidity = mean(Turbidity)) %>%
           ggplot(aes(x = avg_turbidity, y = Beach.Name))+
           geom_point(color = 'red', size = 2)+
           geom_segment(aes(x = 0, xend = avg_turbidity,y = Beach.Name, yend = Beach.Name), color = "blue") + 
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size = 9, face = "bold"),
                 legend.position = "none") + 
           labs(y = "Chicago Beach Location", x = "Average Turbidity (NTU)"))
)
```

Column
------
### Chicago Beach's Average Turbidity by Year and Month

```{r Graph 6 Setup}
renderPlotly(
ggplotly(graph6 <- tidy %>%
           filter(Beach.Name == input$beach_turb) %>%
           select(Turbidity,year_month) %>%
           group_by(year_month) %>%
           summarize(month_avg_turbidity = mean(Turbidity)) %>%
           ggplot(aes(x = month_avg_turbidity, y = year_month))+
           geom_bar(stat = 'identity', fill = "#3A718F")+
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size = 9, face = "bold")) + 
           labs(y = "Year & Month", x = "Average Turbidity (NTU)"))
)
```

Battery Life
======

Input{.sidebar}
-----------------
### Battery Life Graph Input
```{r Battery Life Plot Input}
sliderInput(inputId = "year_battery",
            label = "Select the year ",
            min = min(year_factor),
            max = max(year_factor),
            value = year_factor[1])

selectInput(inputId = "beach_battery",
            label = "Select the beach",
            choices = beach_factor,
            multiple = FALSE,
            selected = beach_factor[4])
```

Column
------
### Chicago Beaches' Battery Life Average per Year

```{r Graph 7 Setup}
renderPlotly(
ggplotly(graph7 <- tidy %>%
           filter(disp_year == input$year_battery) %>%
           select(Battery.Life, Beach.Name) %>%
           group_by(Beach.Name) %>%
           summarize(avg_battery = mean(Battery.Life)) %>%
           ggplot(aes(x = avg_battery, y = Beach.Name))+
           geom_point(color = "#FF9611", size = 2)+
           geom_segment(aes(x = 0, xend = avg_battery, y = Beach.Name, yend = Beach.Name), color = "#1176FF") + 
           theme(axis.text.y = element_text(size = 11),
                 axis.text.x = element_text(size = 11),
                 axis.title = element_text(size = 12, face = "bold"),
                 title = element_text(size =13, face = "bold"),
                 legend.position = "none") + 
           labs(y = "Chicago Beach Location", x = "Average Battery Life for Sensor"))
)
```

Column
------
### Chicago Beach's Battery Life Distribution by Years

```{r Graph 8 Setup}
renderPlotly(
ggplotly(graph8 <- tidy %>%
           filter(Beach.Name == input$beach_battery & disp_year != "2013") %>%
           select(Battery.Life, disp_year) %>%
           group_by(disp_year) %>%
           ggplot(aes(x = disp_year, y = Battery.Life, fill = disp_year)) +
           geom_boxplot() +
           theme(axis.text.y = element_text(size = 9),
                 axis.text.x = element_text(size = 9),
                 axis.title = element_text(size = 9, face = "bold"),
                 title = element_text(size =9, face = "bold"),
                 legend.position = "none") + 
           labs(y = "Battery Life", x = "Year & Month"))
)
```